%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage{ragged2e}

\usepackage{xcolor}
\hypersetup{colorlinks,urlcolor=blue}

%----------FONT OPTIONS----------
\usepackage{charter} % Consistent font throughout

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
    \item\small{
            {#1 \vspace{-2pt}}
    }
}

\newcommand{\achievementItem}[1]{
    \item\small{
            {#1 \vspace{-6pt}}
    }
}

\newcommand{\classesList}[4]{
    \item\small{
            {#1 #2 #3 #4 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textbf{\small #2} \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
        \small#1 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\justify \begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
{\Huge \scshape Abhishek Latawa} \\ \vspace{1pt}
\vspace{5pt}
\small \raisebox{-0.1\height}\faPhone\ +16474072327 ~
\raisebox{-0.2\height}\faEnvelope\ \href{mailto:abhisheklatawa1103@gmail.com}{abhisheklatawa1103@gmail.com} ~
\raisebox{-0.2\height}\faLinkedin\ \href{https://www.linkedin.com/in/abhishek-latawa-a3177b129/}{LinkedIn} ~
\raisebox{-0.2\height}\faGithub\ \href{https://github.com/abhilatawa}{GitHub} ~ \raisebox{-0.2\height}\faGlobe\ \href{https://read.cv/alatawa}{Resume}
\vspace{-8pt}
\end{center}

%-----------PROFILE-----------
\section{Profile}
{With nearly 5 years of experience in financial and banking services as an automation tester, I specialize in cloud operations and automation. Passionate about DevOps, system administration, and leveraging cloud technologies to enhance business agility and efficiency. Key achievement: integrated automated cloud solutions, improving response time to critical issues by 91 percent and enhancing software deployment workflows through CI/CD pipelines.}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Master's of Applied Computer Science}{Sept '23 -- Present}
{Dalhousie University}{Nova Scotia, Canada}
\resumeSubheading
{Bachelor of Technology in Computer Science}{August '14 -- May '18}
{SRM Institute of Science and Technology}{Uttar Pradesh, India}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{{Fiserv India Pvt. Ltd.}\href{https://www.fiserv.com/en-in.html}{}}{Dec '18 -- Aug '23}
{Professional, Quality Assurance Engineering}{}

\vspace{-5pt}
\resumeItemListStart
\resumeItem{Developed and optimized cloud-based validation processes by understanding customer requirements and project KPIs, integrating methodologies such as Smoke, Sanity, Regression, and Unit testing within CI/CD pipelines using GitLab CI.}
\resumeItem{Implemented Azure Virtual Machines (VMs) and CI/CD pipelines to deploy, test, and validate software releases, ensuring seamless integration and enhancing scalability and efficiency across the development lifecycle. This involved setting up infrastructure and defining development, test, release, update, and support processes.}
\resumeItem{Created comprehensive test cases using Selenium and Java, covering all software requirements and contributing to significant improvements in cloud deployment efficiency. Applied troubleshooting techniques to address and fix code issues effectively.}
\resumeItemListEnd

%-----------PROJECTS-----------
\section{Projects}
\vspace{-5pt}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{VirtualVacation} $|$ \emph{Python, DynamoDB, AWS, GCP, Lambda, S3, AWS Cognito, Google Dialogflow}}{}
\setlength{\baselineskip}{5pt}
\resumeItem{A vacation home application that leverages AWS and GCP technologies to provide efficient room booking and availability management using a Virtual Assistant.}
\resumeItemListStart
\resumeItem{Developed the virtual assistant bot utilizing Google Cloud's Dialogflow.}
\resumeItem{Integrated the virtual assistant with the frontend interface.}
\resumeItem{Implemented serverless functionality for bookings using AWS Lambda functions.}
\resumeItem{Created CloudFormation YAML templates to automate service deployments.}
\resumeItemListEnd
\vspace{5pt}
\resumeProjectHeading
{\textbf{MedHub} $|$ \emph{ReactJs, Java Spring Boot, JUnit, AWS S3} $|$ \href{https://github.com/abhilatawa/MedHub}{GitHub}}{}
\setlength{\baselineskip}{5pt}
\resumeItem{A comprehensive healthcare platform designed to streamline patient-doctor interactions and enhance care delivery by connecting patients, doctors, and pharmacists effectively.}
\resumeItemListStart
\resumeItem{ Developed the unit and integration test suites using JUnit, improving software coverage.}
\resumeItem{Managed application deployment through CI/CD pipelines with GitLab, enhancing workflow efficiency.}
\resumeItem{Built a responsive frontend UI using Material-UI and React, ensuring a modern and user-friendly experience.}
\resumeItem{Developed backend scripts for the Rating and Blogs features, integrating them effectively into the service class.}
\resumeItemListEnd

\vspace{5pt}
\resumeProjectHeading
{\textbf{DocShare} $|$ \emph{Python, Boto3 SDK, HTML, CSS, AWS} $|$ \href{https://github.com/abhilatawa/AWS-Cloud-Project_DocShare/tree/main/DocShare}{GitHub}}{}
\setlength{\baselineskip}{5pt}
\resumeItem{A document sharing platform entirely built on AWS services, designed to seamlessly deliver documents directly to users' personal email accounts using serverless architecture.}
\resumeItemListStart
\resumeItem{Created AWS Lambda functions in Python for serverless architecture.}
\resumeItem{Used AWS services like API Gateway, S3, EC2, SNS, and SQS for application workflow.}
\resumeItem{Hosted the frontend using S3 buckets and Amazon EC2, with CI/CD pipelines for continuous delivery and deployment.}
\resumeItem{Automated the entire application using AWS CloudFormation (IAC).}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{
\item \textbf{Languages}: JAVA, Python, HTML, CSS
\item \textbf{Technologies}: ReactJS, Flask, Spring Boot, Kubernetes, Selenium, TestNG
\item \textbf{Tools}: Git, Docker, AWS CloudFormation, Terraform, IntelliJ, ServiceNow, HP-ALM, TFS, SkyTap
\item \textbf{Databases}: MySQL, OracleSQL, DynamoDB
\item \textbf{Methodologies}: Agile, Waterfall, TDD
}
\end{itemize}

%-----------CERTIFICATIONS-----------

\end{document}
